SPIDERMAN: an open source code to model phase curves and secondary eclipses.

### 2017-07-20 ms.tex
Update on Overleaf.

General Circulation Models (GCM's), are currently the state of the art for predicting the wind patters and temperature distributions of the surface of exoplanets \citep[e.g.][]{Showman2008}. An important early prediction of these GCM's was that hot, tidally locked Jupiter's would display significantly offset hotpots. The hotspot offset is the result of fast superotating equatorial winds in the atmosphere that arise from a coupling of planetary scale circulation and day night advection (citation).

An offset hotspot can be detected though the thermal phase-curve of the planet, as the point of maximum flux will be delayed from the time of secondary transit by a measurable amount. This effect can also be mimicked by a high eccentricity \citep{J.deWit2012a} (is this the right citation?).

@@

\textsc{batman} \citep{Kreidberg2015a} is a fast and accurate analytical model of exoplanet primary transits, the code is open source and publicly available. \textsc{batman} serves as the inspiration for this project, as there does not currently exist an open source code for calculating both secondary eclipses and phase curves in a self consistent way, \textsc{spiderman} is designed to fulfil this role, and it is is hoped that it will be of use to the community.

>>>>

General Circulation Models (GCM's), are currently the state of the art for predicting the wind patters and temperature distributions of the surface of exoplanets \citep[e.g.][]{Showman2008}. An important early prediction of these GCM's was that hot, tidally locked Jupiter's would display significantly offset hotpots. The hotspot offset is the result of fast superotating equatorial winds in the atmosphere that arise from a coupling of planetary scale circulation and day night advection \citep{Showman2011}.

An offset hotspot can be detected though the thermal phase-curve of the planet, as the point of maximum flux will be delayed from the time of secondary transit by a measurable amount. This effect can also be mimicked by a high eccentricity. \citet{J.deWit2012a} show that this is not the case for HD\,189733b using eclipse mapping.

@@

\textsc{batman} \citep{Kreidberg2015a} is a fast analytical model of exoplanet primary transits, the code is open source. \textsc{batman}. as there does not currently exist an open source code for calculating both secondary eclipses and phase curves in a self consistent way, \textsc{spiderman} is designed to fulfil this role, and it is is hoped that it will be of use to the community.
